%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}



\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}





\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \small #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Russell Lobo} & 
  \begin{tabular}{r}
    \href{mailto:r.lobo2003@gmail.com}{r.lobo2003@gmail.com}\\
    \href{tel:+447471168554}{+44 7471168554} \\
    \href{https://www.linkedin.com/in/russell-lobo-b295ba147}{linkedin}
  \end{tabular} \\
\end{tabular*}

%-----------PROFILE-----------------
\section{Profile}
  \resumeSubHeadingListStart
    \resumeItem{Builder}
      {Risk Consultant with a track record of deploying novel solutions to fix broken workflows rather than keeping the status quo.}
    \resumeItem{Systems Thinker}
      {Biochemistry graduate who applies scientific rigour. Comfortable translating complex information into actionable insights, presenting to stakeholders, and iterating on solutions based on hypothesis-led testing.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Bristol}{Bristol, UK}
      {Bachelor of Science in Biochemistry; 1:1}{2022 -- 2025}
      \resumeItemListStart
        \resumeItem{Literature Review}
          {Mapping the Unseen: The Quest for Efficient, Automated Organelle Segmentation}
        \resumeItem{Research Project}
          {Dual Nucleotide Specificity of the Recombinant YchF Homologue from Pyrococcus horikoshii}
      \resumeItemListEnd
    % \resumeSubheading
    %   {The London Oratory School}{London, UK}
    %     {Secondary school}{2011 -- 2022}
    %   \resumeItemListStart
    %     \resumeItem{A levels}
    %     {Biology (A*), Chemistry (A), Mathematics (A), Economics AS (A)}
    %     \resumeItem{GCSEs}
    %     {10A*s, 1A}
    %     \resumeItem{Awards}
    %     {Oratory Dux Proxime (for outstanding academic results)}
    %     \resumeItemListEnd  
    
  \resumeSubHeadingListEnd





%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {EY}{London, UK}
      {Risk Consultant}{Sep 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Engineered Internal Audit Tooling}
          {Identified a critical bottleneck in manual evidence review in audits; built and deployed a full-stack Python application (using Tesseract OCR for extraction and LLM APIs for semantic analysis) wrapped in a Tailwind CSS WebUI.}
        \resumeItem{Operational Impact}
          {Scaled the tool to a 8-person engagement team, automating the extraction of unstructured data from PDFs; significantly reduced manual audit cycles while increasing data accuracy and consistency.}
        \resumeItem{Diagnosed Workflows}
          {Conducted deep-dive sessions to map end-to-end audit workflows; translated team feedback into structured process maps to identify friction points.}
      \resumeItemListEnd
    \resumeSubSubheading
      {Consulting Intern}{July 2024}
      \resumeItemListStart
        \resumeItem{Data-Driven Decision Making}
          {Leveraged SQL and PowerBI to turn raw incident management data into a cohesive narrative; pitched recommendations to Partners to drive client decision-making.}
        \resumeItem{On-Site Discovery}
          {Embedded into on-site client teams to capture requirements for Risk \& Control Matrices (RACMs), quickly upskilled to understand the audit landscape.}
        \resumeItem{Performance}
          {Selected from a 3\% acceptance rate applicant pool; secured a return offer based on technical delivery and client impact.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {MyTutor}{Remote}
      {Maths tutor}{October 2022 -- February 2023}
      
      \resumeItemListStart
        \resumeItem{Communication and support}
          {Guided KS2 students in after-school group sessions, addressing each student's specific learning challenges individually. Developed a "first-principles" teaching style to simplify logic.}
      \resumeItemListEnd



    

  \resumeSubHeadingListEnd
  
%-----------VOLUNTEERING-----------------
%\section{Volunteering}
%  \resumeSubHeadingListStart
%  \resumeSubheading
%      {The London Oratory School}{London, UK}
%      {Science tutor and peer mentor}{September 2021 -- March 2022}
%      \resumeItemListStart
%        \resumeItem{Support}
%          {Helped GCSE students removed from class overcome academic challenges.}
%        \resumeItem{Communication}
%          {Stayed calm under pressure while ensuring students felt heard.}
%          
%      \resumeItemListEnd
%  \resumeSubHeadingListEnd
  
%-----------PROJECTS & SKILLS-----------------
\section{Technical Projects \& Skills}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SME Digital Transformation}{Hospitality \& Retail}
      {Full-Stack Deployment}{}
      \resumeItemListStart
        \resumeItem{Full-Stack Deployment}{Architected and deployed a custom, self-hosted reservation system and responsive web frontend for a family-owned restaurant.}
        \resumeItem{Business Impact}{Digitalisation of the booking workflow resulted in a 35\% increase in monthly reservations and reduced admin time by $\sim$8 hours/week.}
        \resumeItem{Scaling}{Currently refactoring the codebase to deploy a bespoke booking and inventory management solution for an upcoming beauty salon client.}
      \resumeItemListEnd

    \resumeSubheading
      {Monopoly Strategy Simulator}{Python}
      {Stochastic Modelling}{}
      \resumeItemListStart
        \resumeItem{Stochastic Modelling}{Built a Python-based simulation engine to model board state probabilities and dice-roll distributions over 10,000+ game iterations.}
        \resumeItem{Strategic Analysis}{Applied statistical analysis to identify optimal property acquisition strategies (a simplified ``Digital Twin'' of the game economy).}
      \resumeItemListEnd
    \item
      \textbf{Self-taught}
      \resumeItemListStart
        \resumeItem{Languages \& Tools}{Agents (Claude Code, Codex), Basic Python (Pandas, Selenium, Requests), R, PowerBI, Tailwind CSS, Git.}
        \resumeItem{Core Competencies}{Rapid Prootyping with agents, Web Scraping/Automation, Process Mapsping.}
        \resumeItem{Learning}{Self-taught developer with a proven ability to upskill rapidly in new languages and agentic workflows to solve immediate business problems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%--------SKILLS------------
%\section{Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, JavaScript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}